Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
edits to induction appendix

\section{Appendix}
\subsection{Inner product of two B-spline scaling functions}\label{ap:InnerProductOfBsplines}
In this section, an analytic formula is derived for the inner product of two B-spline scaling functions. Consider two B-spline scaling functions of order $m$ and $m'$. The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e.
\begin{align}\label{eq:APP-SymmetrySplieEq}
 N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right).
\end{align}
A direct consequence of \eqref{eq:APP-SymmetrySplieEq} is 
\begin{align}
 N_{m}\left(r\right)=N_{m}\left(m-r\right).
\end{align}
Therefore
\begin{align}
\int_{-\infty}^{+\infty}N_{m}\left(r-l_{1}\right)N_{m'}\left(r-l_{2}\right)ds&=\int_{-\infty}^{+\infty}N_{m}\left(m-r+l_{1}\right)N_{m'}\left(r-l_{2}\right)dr \nonumber \\
&=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
&=\left(N_m \ast N_{m'}\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m'+l_{2}-l_{1}\right).
\end{align}
\subsection{Induction}\label{ap:Induction}
For $n_1$ in equation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
\begin{align}
 N_{m}\left(r\right)&=\sum_{n_1=0}^{m} \left[\mathbf p\right]_{n_1} N_{m}\left(2r-n_1\right) \label{eq:App-TwoScalepair1},
  \end{align}
which clearly holds (see \eqref{eq:MRA-TwoScalepair1}). Now assuming \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we have
\begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
 &N_m(r)=\nonumber \\
&\sum_{n_1,n_2, \dots n_{j-1}=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_{j-1}}N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}}),
\end{align}
$N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
\begin{align}\label{eq:AppendixNj-1intermsofNj}
 &N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})=\nonumber \\
&\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}})
\end{align}
Substituting \eqref{eq:AppendixNj-1intermsofNj} in to \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.

>>>>

\section{Appendix}
\subsection{Inner product of two B-spline scaling functions}\label{ap:InnerProductOfBsplines}
In this section, an analytic formula is derived for the inner product of two B-spline scaling functions. Consider two B-spline scaling functions of order $m$ and $m'$. The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e.
\begin{align}\label{eq:APP-SymmetrySplieEq}
 N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right).
\end{align}
A direct consequence of \eqref{eq:APP-SymmetrySplieEq} is 
\begin{align}
 N_{m}\left(r\right)=N_{m}\left(m-r\right).
\end{align}
Therefore
\begin{align}
\int_{-\infty}^{+\infty}N_{m}\left(r-l_{1}\right)N_{m'}\left(r-l_{2}\right)ds&=\int_{-\infty}^{+\infty}N_{m}\left(m-r+l_{1}\right)N_{m'}\left(r-l_{2}\right)dr \nonumber \\
&=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
&=\left(N_m \ast N_{m'}\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m'+l_{2}-l_{1}\right).
\end{align}
\subsection{Scaling function expansion}\label{ap:Induction}  
In this appendix we show by induction that how the scaling function at $j=0$ can be written in terms of the scaling function at level $j$. For $n_1$ in equation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
\begin{align}
 N_{m}\left(r\right)&=\sum_{n_1=0}^{m} \left[\mathbf p\right]_{n_1} N_{m}\left(2r-n_1\right) \label{eq:App-TwoScalepair1},
  \end{align}
which clearly holds from two-scale relation pair (see \eqref{eq:MRA-TwoScalepair1}). Now assuming \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we can write 
\begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
 &N_m(r)=\nonumber \\
&\sum_{n_1,n_2, \dots n_{j-1}=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_{j-1}}N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}}),
\end{align}
in which $N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
\begin{align}\label{eq:AppendixNj-1intermsofNj}
 &N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})=\nonumber \\
&\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}}).
\end{align}
Substituting \eqref{eq:AppendixNj-1intermsofNj} into \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.
